### 2014-12-13 paper.tex

>>>>

  Finally, we find that Stephanopolous and McGhee's simplification of wasted votes into seat share and vote shares simply does not work.  For states where districts are not well-contested, voter efficiency measures can dramatically change from favoring one party slightly to favoring the other party significantly.  In one case, we saw Texas go from approximately one seat pro-democratic, to over two seats pro-republican.  Thus, the wasted votes approach, as the more general case, is much better to use for consistency and accuracy reasons.

  \subsection{Relationship Between Compactness and Bias Measures}
